\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{geometry}

\title{The Rise of Artificial Intelligence}
\author{AI Assistant}
\date{\today}

\begin{document}

\maketitle

\begin{abstract}
This article explores the rapid advancement of Artificial Intelligence (AI), focusing on Machine Learning, Deep Learning, and their transformative impact on various industries.
\end{abstract}

\section{Introduction}
Artificial Intelligence (AI) has evolved from a theoretical concept to a powerful tool driving innovation. From natural language processing to computer vision, AI systems are becoming increasingly sophisticated.

\section{Machine Learning}
At the core of modern AI is Machine Learning (ML). Algorithms learn from data to make predictions or decisions without being explicitly programmed for the task.

\subsection{Neural Networks}
Deep Learning, a subset of ML, utilizes neural networks with many layers. A simple representation of a neuron's output $y$ can be described as:

\begin{equation}
    y = \sigma(\sum_{i=1}^{n} w_i x_i + b)
\end{equation}

Where:
\begin{itemize}
    \item $w_i$ are the weights
    \item $x_i$ are the inputs
    \item $b$ is the bias
    \item $\sigma$ is the activation function
\end{itemize}

\section{Future Implications}
The integration of AI into daily life raises important questions about ethics, privacy, and the future of work. However, its potential to solve complex problems in healthcare, climate change, and education is immense.

\end{document}